### 2017-01-16 papers.tex
Adds details to ind_003

>>>>

\subsection{Reading Notes}

\Gls{lms} are being widely used. Moodle is very famous.

\Gls{lms} store a lot of data regarding student profiles, their grades, when
they login, etc. Analysing this data is hard to do by hand. Data Mining
techniques may be used.

Data Mining has been applied to a variety of problems in e-learning. Like:

\begin{itemize}
    \item Dealing with assessment of students' learning performance.
    \item Providing course adaptations and learning recommendations.
    \item etc. See more at 17
\end{itemize}

The objective of this paper is to classify students with similar final marks
into different groups depending on the activities carried out in a web-based
course.

Data from Cordoba University is used in 7 Moodle engineering courses. The data
comes from three online activities:

\begin{itemize}
    \item Quizzes
    \item Assignments
    \item Forums
\end{itemize}

The data was divided into 10 pairs of training and test data files for
stratified 10-fold cross-validation (reference 81).

The first experiment consists on executing every algorithm with three datasets
and getting the geometric mean:

\begin{itemize}
    \item First dataset. All 438 instances/students with all features.
    \item Second dataset. Filtered instances where students didn't complete
        every Moodle activity. Got 135 instances.
    \item Third dataset. All instance but only with the 4 features which were
        selected using a few methods.
\end{itemize}

The second experiment is basically the same as the first, but the data ha two
pre-processing tasks applied to it: discretization and rebalancing.

Paper also gives some background on data mining. Also talks about Moodle Data
Mining Tool.
